Windowed least-squares model reduction for dynamical systems

### 2019-10-18 section3/space_time.tex
problems in 4.5

%We now briefly consider \spaceTimeAcronym\ trial subspaces. 
The \spaceTimeAcronym\ trial subspace over the $n$th time window approximates
the FOM ODE solution trajectory $\stateFOM\in\RR{N}\otimes\timeSpace$
with $\approxstateArgnt{n} \in \stspaceSTArg{n}$, where
\begin{equation}\label{eq:st_sttrialspace}
 \stspaceSTArg{n} \defeq
 \Range{\stbasisArgnt{n}} + \stateInterceptSTArg{n}\otimes \onesFunctionArg{n} \subseteq \RR{\fomdim} \otimes \timeSpaceArg{n}.
\end{equation}
\EP{Is it wrong to say $\stbasisArg{n}{\cdot} \in \RR{\fomdim \times \stdimArg{n}}$ with $\stbasisArgnt{n}: \timeDummy \mapsto \stbasisArgnt{n}(\timeDummy) \ldots$? I don't particularly like
$\stbasisArgnt{n} \in \RR{\fomdim \times \stdimArg{n}}\otimes\timeSpaceArg{n}$; as the reader I think that $\stbasisArgnt{n}$ can take on all temporal functions.}
Here $\stbasisArgnt{n} \in \RR{\fomdim \times
\stdimArg{n}}\otimes\timeSpaceArg{n}$, $n=1,\ldots,\nslabs$, with $\stbasisArgnt{n}: \timeDummy \mapsto \stbasisArgnt{n}(\timeDummy)$ and $\stbasisArg{n}{\timeStartArg{n}} = \bz$ is the space--time trial basis matrix {function} and $\stateInterceptSTArg{n} \in \RR{\fomdim}$, $n=1,\ldots,\nslabs$ provides the affine transformation. 
To enforce the initial condition and ensure solution continuity across time windows, we set $\stateInterceptSTArg{1} = \stateFOMIC$ and
$\stateInterceptSTArg{n} = \approxstateArg{n-1}{\timeEndArg{n-1}}$ for
$n=2,\ldots,\nslabs$.
At any time instance $t \in [\timeStartArg{n},\timeEndArg{n}]$, the \spaceTimeAcronym\ trial subspace approximates the FOM ODE solution as
 \begin{equation}\label{eq:stapprox}
 \stateFOMArg{n}{t} \approx \approxstateArg{n}{t}  = \stbasisArg{n}{t} \stgenstateArg{n} + \stateInterceptSTArg{n},
\end{equation}
where $\stgenstateArg{n} \in \RR{\stdimArg{n}}$ are the space--time generalized coordinates over the $n$th window. 
\begin{comment}
each window, we introduce the space--time trial subspace
$$ \stateArgnt{n} \in \stspaceSTArg{n} \subseteq \RR{N} \otimes \timeSpaceArg{n},$$
along with the space--time trial basis matrix \textit{function}, 
\begin{align*}
\stbasisArgnt{n} &: t \mapsto \stbasis(t) \\
 &: [\timeStartArg{n},\timeEndArg{n}] \rightarrow  \RR{N \times \stdimArg{n}}  ,%\spaceTrialSpace , \\
\end{align*}
\KTC{shouldn't be $\equiv$. Look earlier for this. the right hand side should
be on the left with $\defeq$.} with $\Range{\stbasisArgnt{n}} + \stateInterceptSTArg{} \equiv \stspaceSTArg{n} $ and where $\stdimArg{n}$ is the number of space--time generalized coordinates over the $n$th window. 
For simplicity we assume the reference state to be equivalent for each time window, although no such requirement is necessary. 
\KTC{Remove all commas before equations unless it makes sense gramatically.
Add the $n$ superscript to $x_{ref}$}
The state over each window is approximated by,
\begin{equation}\label{eq:stapprox}
 \stateFOMArg{n}{t} \approx \approxstateArg{n}{t}  = \stbasisArg{n}{t} \stgenstateArg{n} + \stateInterceptSTArg{},
\end{equation}
%and the state is then approximated by,
%\begin{equation}\label{eq:stapprox}
% \stateArg{n}{t} \approx \approxstateArg{n}{t}  = \stbasisArg{n}{t} \stgenstate + \stateInterceptArg{n},
%\end{equation}
%where $\stgenstateArg{n} \in \RR{\stdimArg{n}}$ are the space--time generalized coordinates over the $n$th window.

>>>>

%We now briefly consider \spaceTimeAcronym\ trial subspaces. 
The \spaceTimeAcronym\ trial subspace over the $n$th time window approximates
the FOM ODE solution trajectory $\stateFOM\in\RR{N}\otimes\timeSpace$
with $\approxstateArgnt{n} \in \stspaceSTArg{n}$, where
\begin{equation}\label{eq:st_sttrialspace}
 \stspaceSTArg{n} \defeq
 \Range{\stbasisArgnt{n}} + \stateInterceptSTArg{n}\otimes \onesFunctionArg{n} \subseteq \RR{\fomdim} \otimes \timeSpaceArg{n}.
\end{equation}
\EP{Is it wrong to say $\stbasisArg{n}{\cdot} \in \RR{\fomdim \times \stdimArg{n}}$ with $\stbasisArgnt{n}: \timeDummy \mapsto \stbasisArgnt{n}(\timeDummy) \ldots$? I don't particularly like
$\stbasisArgnt{n} \in \RR{\fomdim \times
\stdimArg{n}}\otimes\timeSpaceArg{n}$; as the reader I think that
$\stbasisArgnt{n}$ can take on all temporal functions.} \KTC{I'm not
understanding why this is confusing. We previously said that a time dependent
$n$-vector is $\RR{n}\otimes \timeSpaceArg{n}$. This is the same exact thing
except for a time-dependent matrix.}
Here $\stbasisArgnt{n} \in \RR{\fomdim \times
\stdimArg{n}}\otimes\timeSpaceArg{n}$, $n=1,\ldots,\nslabs$, with $\stbasisArgnt{n}: \timeDummy \mapsto \stbasisArgnt{n}(\timeDummy)$ and $\stbasisArg{n}{\timeStartArg{n}} = \bz$ is the space--time trial basis matrix {function} and $\stateInterceptSTArg{n} \in \RR{\fomdim}$, $n=1,\ldots,\nslabs$ provides the affine transformation. 
To enforce the initial condition and ensure solution continuity across time windows, we set $\stateInterceptSTArg{1} = \stateFOMIC$ and
$\stateInterceptSTArg{n} = \approxstateArg{n-1}{\timeEndArg{n-1}}$ for
$n=2,\ldots,\nslabs$.
At any time instance $t \in [\timeStartArg{n},\timeEndArg{n}]$, the \spaceTimeAcronym\ trial subspace approximates the FOM ODE solution as
 \begin{equation}\label{eq:stapprox}
 \stateFOMArg{n}{t} \approx \approxstateArg{n}{t}  = \stbasisArg{n}{t} \stgenstateArg{n} + \stateInterceptSTArg{n},
\end{equation}
where $\stgenstateArg{n} \in \RR{\stdimArg{n}}$ are the space--time generalized coordinates over the $n$th window. 
\begin{comment}
each window, we introduce the space--time trial subspace
$$ \stateArgnt{n} \in \stspaceSTArg{n} \subseteq \RR{N} \otimes \timeSpaceArg{n},$$
along with the space--time trial basis matrix \textit{function}, 
\begin{align*}
\stbasisArgnt{n} &: t \mapsto \stbasis(t) \\
 &: [\timeStartArg{n},\timeEndArg{n}] \rightarrow  \RR{N \times \stdimArg{n}}  ,%\spaceTrialSpace , \\
\end{align*}
\KTC{shouldn't be $\equiv$. Look earlier for this. the right hand side should
be on the left with $\defeq$.} with $\Range{\stbasisArgnt{n}} + \stateInterceptSTArg{} \equiv \stspaceSTArg{n} $ and where $\stdimArg{n}$ is the number of space--time generalized coordinates over the $n$th window. 
For simplicity we assume the reference state to be equivalent for each time window, although no such requirement is necessary. 
\KTC{Remove all commas before equations unless it makes sense gramatically.
Add the $n$ superscript to $x_{ref}$}
The state over each window is approximated by,
\begin{equation}\label{eq:stapprox}
 \stateFOMArg{n}{t} \approx \approxstateArg{n}{t}  = \stbasisArg{n}{t} \stgenstateArg{n} + \stateInterceptSTArg{},
\end{equation}
%and the state is then approximated by,
%\begin{equation}\label{eq:stapprox}
% \stateArg{n}{t} \approx \approxstateArg{n}{t}  = \stbasisArg{n}{t} \stgenstate + \stateInterceptArg{n},
%\end{equation}
%where $\stgenstateArg{n} \in \RR{\stdimArg{n}}$ are the space--time generalized coordinates over the $n$th window.

### 2019-10-18 section4/spacetime_numerical.tex
problems in 4.5

\subsection{\spaceTimeAcronym\ trial spaces: direct and indirect methods}
We now consider \spaceTimeAcronym\ trial subspaces. 
For \spaceTimeAcronym\ trial subspaces, the distinction between a direct and indirect method is less clear as the optimization variable (i.e., the generalized coordinates) are finite 
dimensional. There is no need to transcribe an infinite dimensional optimization variable into a finite dimensional one. There is, however, still a need to develop a finite 
dimensional representation of the objective functional~\eqref{eq:obj_gen_slab}. We describe two techniques to do this: one that works with the FOM O$\Delta$E and one that works with the FOM ODE. We associate direct methods as those 
that work with the O$\Delta$E and indirect methods with those that work directly with the ODE.

\subsection{\spaceTimeAcronym: direct solution approach}
The direct solution technique seeks to minimize the fully discrete objective function associated with the O$\Delta$E. For brevity, we focus on linear multistep methods and leverage the time grids introduced in Section~\ref{sec:direct}. For notational simplicity, we define an index mapping function that is 
equivalent to the mapping function $\indexMapper$, but outputs only the first argument: 
$$\indexMappern: (n,i) \mapsto 
\begin{cases}
n & n = 1, \; i = 0, \\
n & n \ge 1, \; i > 0, \\
\indexMappern(n-1,\nstepsArg{n-1}+i) & n > 1, \; i \le 0.
\end{cases}$$
%The definition of the fully discrete objective functions~\eqref{eq:obj_lms} as outlined in Section~\ref{sec:direct}, can be leveraged for this purpose. For simplicity, we only 
%outline the case for linear multistep schemes. 
Assuming $\text{Rank}(\stweightingMatOneArg{n})\nstepsArg{n} \ge \stdimArg{n}$, \methodAcronym\ with the direct approach and an \spaceTimeAcronym\ trial subspace sequentially computes the generalized coordinates $\stgenstateArg{n}$, $n=1,\ldots,\nslabs$ that satisfy
 \begin{equation}\label{eq:obj_gen_lms_final_st}
\begin{split}
& \underset{\stgenstatey \in \RR{\stdimArg{n}}}{\text{minimize } }
\objectiveArgLMS{n}_{\text{D-ST}} (\stbasisArg{n}{\timeWindowArg{n}{1}} \stgenstatey + \stateInterceptSTArg{n},\ldots,\stbasisArg{n}{\timeWindowArg{n}{\nstepsArg{n}}} \stgenstatey + \stateInterceptSTArg{n}),%  \\
%&\text{subject to } \;  \stbasisArg{n}{\timeStartArg{n}}\stgenstateyArg{n} = \begin{cases} 
%\mathbb{P}^n(\stbasisArgnt{n-1}\stgenstateArg{n-1})(\timeEndArg{n-1}) & n = 2,\ldots,\nslabs, \\ 
%\mathbb{P}^n(\stateFOMArgnt{1})(0) &
%n=1. \end{cases}
\end{split} 
\end{equation}
where the space--time objective function for the direct method is
$$
\objectiveArgLMS{n}_{\text{D-ST}}  :  (\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \mapsto \objectiveArgLMS{n}_{\text{D}}(\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}; \approxstateArg{\indexMappern(n,0)}{\timeWindow^{\indexMapper(n,0)}},\ldots, 
 \approxstateArg{\indexMappern(n,-\lmsWidthArg{n}{1}+1)}{\timeWindow^{\indexMapper(n,-\lmsWidthArg{n}{1}+1)}}).
$$
The boundary conditions are automatically satisfied through the definition of the \spaceTimeAcronym\ trial subspace. The minimization problem~\eqref{eq:obj_gen_lms_final_st} again yields a least-squares problem.
\begin{remark}
For the limiting case where one window comprises entire domain (i.e., $\DeltaSlabArg{1}\equiv T$), uniform quadrature weights are used, the trial space is set to be $\stspaceSTArg{1} = \stspaceST$, the weighting matrices $\stweightingMatArg{1}$ and $\lspgWeightingST$ comprise the identity matrix $\mathbf{I}$, and $\nstepsArg{1} = N_t$ time instances are employed that satisfy $\timeWindowArg{1}{i} = t^i$, $i=1,\ldots,N_t$, then $\stgenstateArg{1} =  \stgenstate_\text{ST-LSPG}$ and direct \methodAcronym\ with an \spaceTimeAcronym\ trial subspace recovers ST-LSPG. 
\end{remark}

@@

\subsection{\spaceTimeAcronym: indirect solution approach}

@@

discretization of the integral. Towards this end we introduce $\ncollocSTArg{n} \ge \text{ceil}(\stdimArg{n}/ \text{Rank}(\stweightingMatOneArg{n}))$ quadrature points over the $n$th window, $ \{ \collocPointSTArg{n}{i} \}_{i=1}^{\ncollocSTArg{n}} \subset [\timeStartArg{n},\timeEndArg{n}]$, $n=1,\ldots,\nslabs$. 

@@

\subsection{\spaceTimeAcronym\: summary}

>>>>

\subsection{\spaceTimeAcronym\ trial subspaces: direct and indirect methods}
We now consider \spaceTimeAcronym\ trial subspaces.  Because the optimization
variables (i.e., the generalized coordinates) in this case are already finite
dimensional, solvers for this type of trial subspace need only develop a
finite-dimensional representation of the objective
functional in problem~\eqref{eq:obj_gen_slab_spacetime}. We describe two
techniques for this purpose: a direct method 
that operates on the FOM O$\Delta$E and an indirect method that operates on the FOM ODE.

\subsection{\spaceTimeAcronym\ trial subspaces: direct solution approach}
\KTC{Fix this section:
\begin{enumerate} 
\item remove $\theta^\star$
\item replace $J_{D-ST}^n$ in (38) with $J_D^n$. You can do this because of Eq
	(33)
\item remove definition of $J_{D-ST}$.
 \end{enumerate}
}
The direct solution technique seeks to minimize the fully discrete objective
function associated with the FOM O$\Delta$E. For brevity, we focus on linear
multistep methods and leverage the time grids introduced in
Section~\ref{sec:direct}. For notational simplicity, we define an
index-mapping function that is equivalent to the mapping function
$\indexMapper$, but outputs only the first argument: 
$$\indexMappern: (n,i) \mapsto 
\begin{cases}
n & n = 1, \; i = 0, \\
n & n \ge 1, \; i > 0, \\
\indexMappern(n-1,\nstepsArg{n-1}+i) & n > 1, \; i \le 0.
\end{cases}$$
%The definition of the fully discrete objective functions~\eqref{eq:obj_lms} as outlined in Section~\ref{sec:direct}, can be leveraged for this purpose. For simplicity, we only 
%outline the case for linear multistep schemes. 
\methodAcronym\ with an \spaceTimeAcronym\ trial subspace and the direct approach sequentially computes the generalized coordinates $\stgenstateArg{n}$, $n=1,\ldots,\nslabs$ that satisfy
 \begin{equation}\label{eq:obj_gen_lms_final_st}
\begin{split}
& \underset{\stgenstatey \in \RR{\stdimArg{n}}}{\text{minimize } }
\objectiveArgLMS{n}_{\text{D-ST}} (\stbasisArg{n}{\timeWindowArg{n}{1}} \stgenstatey + \stateInterceptSTArg{n},\ldots,\stbasisArg{n}{\timeWindowArg{n}{\nstepsArg{n}}} \stgenstatey + \stateInterceptSTArg{n}),%  \\
%&\text{subject to } \;  \stbasisArg{n}{\timeStartArg{n}}\stgenstateyArg{n} = \begin{cases} 
%\mathbb{P}^n(\stbasisArgnt{n-1}\stgenstateArg{n-1})(\timeEndArg{n-1}) & n = 2,\ldots,\nslabs, \\ 
%\mathbb{P}^n(\stateFOMArgnt{1})(0) &
%n=1. \end{cases}
\end{split} 
\end{equation}
where the space--time objective function for the direct method is defined as
$$
\objectiveArgLMS{n}_{\text{D-ST}}  :  (\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \mapsto \objectiveArgLMS{n}_{\text{D}}(\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}; \approxstateArg{\indexMappern(n,0)}{\timeWindow^{\indexMapper(n,0)}},\ldots, 
 \approxstateArg{\indexMappern(n,-\lmsWidthArg{n}{1}+1)}{\timeWindow^{\indexMapper(n,-\lmsWidthArg{n}{1}+1)}}).
$$
The boundary conditions are automatically satisfied through the definition of the \spaceTimeAcronym\ trial subspace. The minimization problem~\eqref{eq:obj_gen_lms_final_st} again yields a least-squares problem.
\begin{remark}
For the limiting case where one window comprises entire domain (i.e., $\DeltaSlabArg{1}\equiv T$), uniform quadrature weights are used, the trial space is set to be $\stspaceSTArg{1} = \stspaceST$, the weighting matrices $\stweightingMatArg{1}$ and $\lspgWeightingST$ comprise the identity matrix $\mathbf{I}$, and $\nstepsArg{1} = N_t$ time instances are employed that satisfy $\timeWindowArg{1}{i} = t^i$, $i=1,\ldots,N_t$, then $\stgenstateArg{1} =  \stgenstate_\text{ST-LSPG}$ and direct \methodAcronym\ with an \spaceTimeAcronym\ trial subspace recovers ST-LSPG. 
\end{remark}

@@

\subsection{\spaceTimeAcronym\ trial subspaces: indirect solution approach}

@@

discretization of the integral. Towards this end we introduce $\ncollocSTArg{n} \ge \text{ceil}(\stdimArg{n}/ \text{rank}(\stweightingMatOneArg{n}))$ quadrature points over the $n$th window, $ \{ \collocPointSTArg{n}{i} \}_{i=1}^{\ncollocSTArg{n}} \subset [\timeStartArg{n},\timeEndArg{n}]$, $n=1,\ldots,\nslabs$. 

@@

\subsection{\spaceTimeAcronym\ trial subspaces: summary}

### 2019-10-18 section4/spatial_numerical.tex
problems in 4.5

\methodAcronym\ with the direct approach and a linear multistep method sequentially computes the solutions
$\approxstateDiscreteArg{n,1},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}}$,
$n=1,\ldots,\nslabs$, that satisfy
%	\KTC{What is $\genstate^{n-1}(\timeEndArg{n-1} ) $ doing here? Two problems
%	(1) there is no notion of a generalized coordinate $\genstate$ yet, and (2)
%	this should be the discrete solution, not the exact solution evaluated at
%	the final time.} \EP{You are correct, I think there is an error now in the minimize term though. It was $\in \trialspace\otimes \RR{\lmsWidthArg{n}{i}+1}$, it should be $\trialspace\otimes \RR{\nstepsArg{n}+1}$}
\begin{align*}
	&\underset{(\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \in ( \trialspace + \stateInterceptArg{n}) \otimes \RR{\nstepsArg{n}}}{\text{minimize } }
\objectiveArgLMS{n}_{\text{D-S}} (\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}), 
%%& \text{subject to} \hspace{0.2 in}  \stateyDiscreteArg{0} =
%%\begin{cases} \basisspaceArg{n} \spatialICDiscrete + \stateInterceptArg{n}& n = 2,\ldots,\nslabs,\\
%\basisspaceArg{1} \genstateICOne  + \stateInterceptArg{1}& n=1. \end{cases} 
\end{align*}
where
\begin{equation*}
\begin{split}
\objectiveArgLMS{n}_{\text{D-S}} &\vcentcolon  (\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \mapsto \objectiveArgLMS{n}(\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}; \approxstateDiscreteArg{\indexMapper(n,0)},\ldots,\approxstateDiscreteArg{\indexMapper(n,-\lmsWidthArg{n}{1}+1)}), \\
&\vcentcolon \RR{\fomdim} \otimes \RR{\nstepsArg{n}} \rightarrow \RR{}_+,
\end{split}
\end{equation*}
with the initial condition $\approxstateDiscreteArg{1,0} = \basisspaceArg{n}\basisspaceTArg{n} (\stateFOMIC - \stateInterceptArg{n}) + \stateInterceptArg{n}$.
%We additionally set $\approxstateDiscreteArg{1,0} = \projectorSpatialArg{n}(\stateFOMIC)$, where
%$\projectorSpatialArg{n} : \RR{\fomdim} \rightarrow \trialspaceArg{n}$ is the $\elltwo$-orthogonal projector 
%$$\projectorSpatialArg{n} : \stateyDiscreteArgnt{} \mapsto  \basisspaceArg{n}\basisspaceTArg{n} (\stateyDiscreteArgnt{} - \stateInterceptArg{n}) + \stateInterceptArg{n} .$$

@@

\item \textit{Automatic differentiation}: A more intrusive, but exact
	method for computing these terms is
		through automatic differentiation (AD), which evaluate derivatives of
		functions (e.g., Jacobians, vector-Jacobian products) in a numerically
		exact manner by recursively applying the chain rule. The numerical
		examples presented later in this work leverage AD. The principal drawback
		of this approach is their intrusiveness, which may prevent them from
		practical application, e.g., in legacy codes.
		\KTC{EP: verify this paragraph.} \EP{This looks good to me}
\end{enumerate}

\KTC{HERE}
\begin{remark}\label{remark:fbsm}(Acceleration of Indirect Methods)
The FBSM is a simple iterative method for solving the coupled two-point boundary value problem. For large time windows, however, the FBSM may require many 
forward--backward iterations for convergence. More sophisticated solution techniques, such as a multiple FBSM method or multiple shooting methods, promise 
to reduce this cost. Analyses of additional solution techniques will be a subject of future work.
\end{remark}

>>>>

\methodAcronym\ with the direct approach and a linear multistep method sequentially computes the solutions
$\approxstateDiscreteArg{n,1},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}}$,
$n=1,\ldots,\nslabs$, that satisfy
%	\KTC{What is $\genstate^{n-1}(\timeEndArg{n-1} ) $ doing here? Two problems
%	(1) there is no notion of a generalized coordinate $\genstate$ yet, and (2)
%	this should be the discrete solution, not the exact solution evaluated at
%	the final time.} \EP{You are correct, I think there is an error now in the minimize term though. It was $\in \trialspace\otimes \RR{\lmsWidthArg{n}{i}+1}$, it should be $\trialspace\otimes \RR{\nstepsArg{n}+1}$}
\begin{align*}
	&\underset{(\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \in ( \trialspace + \stateInterceptArg{n}) \otimes \RR{\nstepsArg{n}}}{\text{minimize } }
\objectiveArgLMS{n}_{\text{D-S}} (\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}), 
%%& \text{subject to} \hspace{0.2 in}  \stateyDiscreteArg{0} =
%%\begin{cases} \basisspaceArg{n} \spatialICDiscrete + \stateInterceptArg{n}& n = 2,\ldots,\nslabs,\\
%\basisspaceArg{1} \genstateICOne  + \stateInterceptArg{1}& n=1. \end{cases} 
\end{align*}
where
\begin{equation*}
\begin{split}
\objectiveArgLMS{n}_{\text{D-S}} &\vcentcolon  (\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \mapsto \objectiveArgLMS{n}(\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}; \approxstateDiscreteArg{\indexMapper(n,0)},\ldots,\approxstateDiscreteArg{\indexMapper(n,-\lmsWidthArg{n}{1}+1)}), \\
&\vcentcolon \RR{\fomdim} \otimes \RR{\nstepsArg{n}} \rightarrow \RR{}_+,
\end{split}
\end{equation*}
\KTC{On the RHS, shouldn't this be $\objectiveArgLMS{n}_\text{D}$? I couldn't
find the definition of $\objectiveArgLMS{n}$ anywhere.}
with the initial condition $\approxstateDiscreteArg{1,0} = \basisspaceArg{n}\basisspaceTArg{n} (\stateFOMIC - \stateInterceptArg{n}) + \stateInterceptArg{n}$.
%We additionally set $\approxstateDiscreteArg{1,0} = \projectorSpatialArg{n}(\stateFOMIC)$, where
%$\projectorSpatialArg{n} : \RR{\fomdim} \rightarrow \trialspaceArg{n}$ is the $\elltwo$-orthogonal projector 
%$$\projectorSpatialArg{n} : \stateyDiscreteArgnt{} \mapsto  \basisspaceArg{n}\basisspaceTArg{n} (\stateyDiscreteArgnt{} - \stateInterceptArg{n}) + \stateInterceptArg{n} .$$

@@

\item \textit{Automatic differentiation}: A more intrusive, but exact
	method for computing these terms is
		through automatic differentiation (AD), which evaluate derivatives of
		functions (e.g., Jacobians, vector-Jacobian products) in a numerically
		exact manner by recursively applying the chain rule. The numerical
		examples presented later in this work leverage AD. The principal drawback
		of this approach is their intrusiveness, which may prevent them from
		practical application, e.g., in legacy codes.
\end{enumerate}

\begin{remark}\label{remark:fbsm}(Acceleration of Indirect Methods)
The FBSM is a simple iterative method for solving the coupled two-point boundary value problem. For large time windows, however, the FBSM may require many 
forward--backward iterations for convergence. More sophisticated solution
	techniques, such as a multiple FBSM method or multiple shooting methods, can 
reduce this cost in principle. Analyzing additional solution techniques is
	the subject of future work.
\end{remark}
